Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-17 TACAS2018/paper.tex
Clarification

In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
reachable form and the observer error dynamics in observable form. Let 
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}' \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\nonumber\\
\vec{y}_k
=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
where
{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
%\begin{align*}
%
%\mat{A}_{c}=&\left[
%\begin{array}{ccccc}
%0&1&0&\cdots&0\\
%0&0&1&\cdots&0\\
%\vdots&\vdots&\vdots&\ddots&\vdots\\
%0&0&0&\cdots&1\\
%k_n-a_n&\cdots&k_i-a_i&\cdots&k_1-a_1
%\end{array}\right]
%\label{eq:cf_SISO_2}
%\end{align*}
\begin{align*}
\mat{A}_{c}=\left[
\begin{array}{cc}
k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}\\
\mat{I}&\mat{0}
\end{array}\right]&&
\mat{A}_{o}=\left[
\begin{array}{ccc}
a_n-l_n&&\mat{I}\\
&&\vdots\\
a_1-l_1&&\mat{0}
\end{array}\right]
\end{align*}
}
{\setlength{\belowdisplayskip}{0pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}

>>>>

We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e. with dynamics whose coefficients are represented solely by those of the characteristic polynomial as follows:
\begin{align*}
\mat{A}_{c}=\left[
\begin{array}{cc}
k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}\\
\mat{I}&\mat{0}
\end{array}\right]&&
\mat{A}_{o}=\left[
\begin{array}{ccc}
a_n-l_n&&\mat{I}\\
&&\vdots\\
a_1-l_1&&\mat{0}
\end{array}\right]
\end{align*}
where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant.
This is achieved by the following transformation. Let
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}' \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\nonumber\\
\vec{y}_k
=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
{%\setlength{\belowdisplayskip}{0pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}
